Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2016-01-26 latex/article.tex
minor

Volumetric objects are being more and more popular in many
applications ranging from object modeling and rendering in Computer
Graphics to geometry processing in Medical Imaging or Material
Sciences. When considering large volumetric data, interactive
%visualization of such images (or isovalue surfaces) is a complex
visualization of those objects (or isosurfaces) is a complex
problem. Such issues become even more difficult when dynamic
%volumetric datasets are considered. Beside such isosurface
volumetric datasets are considered. Beside
visualization, we are also interested in performing geometry
processing on the digital object and to explore different parameter
settings of the geometry processing tool.
\txtblue{
Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
directions, \ldots). Most curvature estimators require a parameter fixing the scale
at which the computation is performed. For short, such parameter
(integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface,
and is naturally related to the amount allowed perturbations on input
data. As a consequence, when using
such estimators, exploring different values of this parameter is mandatory.
However, this is usually an offline process, due to the amount of computations that
need to be done.}
%In this work, we present an interactive visualization of volumetric data isosurfaces combined with
%a curvature tensor (mean/Gaussian curvature, principal curvatures
%directions, \ldots) estimation at each point of the digital
%surface.
%Curvature maps on a given isosurface are key information when
%exploring 3D structures in Material Sciences \todo{REF}.

>>>>

Volumetric objects are being more and more popular in many
applications ranging from object modeling and rendering in Computer
Graphics to geometry processing in Medical Imaging or Material
Sciences. When considering large volumetric data, interactive
%visualization of such images (or isovalue surfaces) is a complex
visualization of those objects (or isosurfaces) is a complex
problem. Such issues become even more difficult when dynamic
%volumetric datasets are considered. Beside such isosurface
volumetric datasets are considered. Beside
visualization, we are also interested in performing geometry
processing on the digital object and to explore different parameter
settings of the geometry processing tool.
\txtblue{
Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
directions\ldots). Most curvature estimators require a parameter fixing the scale
at which the computation is performed. For short, such parameter
(integration radius, convolution kernel size\ldots) specifies a scale for analyzing the object surface,
and is naturally related to the amount allowed perturbations on input
data. As a consequence, when using
such estimators, exploring different values of this parameter is mandatory.
However, this is usually an offline process, due to the amount of computations that
need to be done.}
%In this work, we present an interactive visualization of volumetric data isosurfaces combined with
%a curvature tensor (mean/Gaussian curvature, principal curvatures
%directions, \ldots) estimation at each point of the digital
%surface.
%Curvature maps on a given isosurface are key information when
%exploring 3D structures in Material Sciences \todo{REF}.
